%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% 	Template for Producing ASP-DAC 2019 Proceedings
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[twocolumn]{article}
%% If you use dvips and ps2pdf, please use Postscript font
%% and uncomment the line below.
%%\usepackage{times}

% % % Packages Add by Louis % % %
\usepackage{comment}
\usepackage{subfigure}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{rotating}
\usepackage{lscape} 
%\usepackage[colorlinks=true, allcolors=black]{hyperref}
\usepackage{pgfplots, pgfplotstable}
\usepackage{tikz}
\usepackage{xcolor}
\usetikzlibrary{trees}
\usetikzlibrary{snakes,arrows,shapes}
\usepackage{textcomp}
\usepackage{listings}
\definecolor{lightgray}{rgb}{0.95, 0.95, 0.95}
\definecolor{darkgray}{rgb}{0.4, 0.4, 0.4}
\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
\definecolor{ocherCode}{rgb}{1, 0.5, 0} % #FF7F00 -> rgb(239, 169, 0)
\definecolor{blueCode}{rgb}{0, 0, 0.93} % #0000EE -> rgb(0, 0, 238)
\definecolor{greenCode}{rgb}{0, 0.6, 0} % #009900 -> rgb(0, 153, 0) 

\usepackage[ruled]{algorithm2e}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{todonotes}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{siunitx}
\sisetup{per=slash, load=abbr}
\usepackage{calc}
\usepackage{array}
\usepackage{caption}
\usepackage{url}
\usepackage{pgf}
\usepackage{mdwlist}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{dot2texi}
\usepackage{graphicx,stfloats}
\usepackage{graphicx,epstopdf}
\epstopdfsetup{update}
\usepackage{enumerate}
% % % Packages Add by Louis % % % 

\pagestyle{empty}
%set paper size
%for A4 paper
\topmargin      29mm    %bottom margin 30mm
\oddsidemargin  15mm    %left & right margin 15mm

%for 8 1/2" x 11" paper paper, use the following definition
%\topmargin     17mm    %bottom margin 24mm
%\oddsidemargin 18mm    %left margin 18mm & right margin 17mm

%text sizes
\textwidth  180mm
\textheight 238mm
\columnsep  5.0mm
\parindent  3.5mm

%misc parameters
\headsep 0mm  \headheight 0mm
\footskip 18mm
%\footheight 6mm

%conversion to values for LaTeX
\advance\topmargin-1in\advance\oddsidemargin-1in
\evensidemargin\oddsidemargin

\makeatletter
%as Latex considers descenders in its calculation of interline spacing,
%to get 12 point spacing for normalsize text, must set it to 10 points
\def\@normalsize{\@setsize\normalsize{12pt}\xpt\@xpt
\abovedisplayskip 10pt plus2pt minus5pt\belowdisplayskip \abovedisplayskip
\abovedisplayshortskip \z@ plus3pt\belowdisplayshortskip 6pt plus3pt
minus3pt\let\@listi\@listI}

%interline spaceing and title font for section
\def\section{\@startsection {section}{1}{\z@}{20pt plus 2pt minus 2pt}
{8pt plus 2pt minus 2pt}{\centering\normalsize\sc
\edef\@svsec{\thesection.\ }}}
\def\thesection{\Roman{section}}

%interline spacing and title font for subsection
\def\subsection{\@startsection {subsection}{2}{\z@}{16pt plus 2pt minus 2pt}
{6pt plus 2pt minus 2pt}{\normalsize\sl
\edef\@svsec{\thesubsection.\ }}}
\def\thesubsection{\Alph{subsection}}

%figures/tables captions
\long\def\@makecaption#1#2{
\vskip10pt\begin{center} #1 #2 \end{center}\par\vskip 1pt}
\def\fnum@figure{\raggedright{\footnotesize Fig. \thefigure }.%
\footnotesize}
\def\fnum@table{\footnotesize TABLE \thetable\\\footnotesize\sc}
\def\thetable{\Roman{table}}

\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%date not printed
\date{}

%make title
\title{\Large\textbf{A High-Performance FPGA Accelerator Framework\\ for Linear Time-Multiplexed Overlays}\\~\\
}

%for single author
%\author{Center the Authors Names Here \\
%Center the Affiliations Here\\
%Center the City, Stats and Country Here\\
%{\small (it is your option if you want your entire address listed)}}

%for two authors
\author{
\\ % To make more spaces just add \\!
}
\maketitle
\thispagestyle{empty}

{\small\textbf{Abstract---
Coarse-grained FPGA overlays have shown promising advantages such as software-like programmability and fast compilation to improve the design productivity. 
However, few of the existing overlays have been developed as complete accelerator systems, suitable for real-world applications. 
To address this issue, a high-performance overlay system framework is proposed, based on two different memory interfaces, AXI and PCIe. 
We implement these hardware accelerators on ZedBoard (AXI-based) and VC707 (PCIe-based) platforms respectively, and evaluate their throughput and resource usage for a range of benchmarks. 
The proposed AXI-Xillybus-Overlay system achieves a much more area efficient implementation in comparison with a state-of-art time-multiplexed (TM) overlay, namely VectorBlox MXP, at the cost of around 50\% of the throughput.
%which is limited by the 32-bit AXI-ACP interface used by AXI-Xillybus compared to the full 64-bit AXI-HP interface used by VectorBlox MXP. 
The proposed RIFFA-Overlay system shows the highest performance among all the proposed overlay accelerators (3.6$\times$ higher than PCIe-Xillybus-Overlay, and 5.7$\times$ better than AXI-Xillybus-Overlay), but at the expense of a larger resource usage on the BRAMs. 
}}

\input{Files/1_introduction}
\input{Files/2_related_work}
\input{Files/3_overlay}
\input{Files/4_system}
\input{Files/5_experiments}
\input{Files/6_discussion}
\input{Files/7_conclusion}

%this is how to do an unnumbered subsection
\section*{\sc Acknowledgements}
This work is supported by the Singapore Ministry of Education (MOE) Academic Research Fund Tier 2 under grant MOE2017-T2-1-002.

\bibliographystyle{acm}
\footnotesize{
\bibliography{Files/references}}

\end{document}
